
Going to download libaries and datasets and explore them

```{r}
## Downloading the necessary libraries
library(readr)
library(dplyr)
library(ggplot2)
library(GGally)
library(tidyr)
library(xlsx)

## Downloading initial datasets
stream.now.orig = read_csv('MoviesOnStreamingPlatforms_updated.csv')
disney = read_csv('disney_movies_total_gross.csv')

## Making the df get rid of columns we don't care about
stream.now = stream.now.orig %>% select(-c(X1,ID))
stream.now = stream.now %>% select(1:5)

## Making sure to standardize the title column and to only have alphanumerics
stream.now$Title = trimws(gsub("[^[:alnum:]]", " ", stream.now$Title))
```


Now exploring the Disney dataset:

```{r}
## Checking type of variables in Disney df
str(disney)

## Making the release data only show the year
disney$release_date = format(disney$release_date, "%Y")

## Getting rid of columns we don't care about
disney = disney %>% select(-c(genre,mpaa_rating,total_gross))

## Making sure to standardize the title column and to only have alphanumerics
disney$movie_title = trimws(gsub("[^[:alnum:]]", " ", disney$movie_title))

```


Because I'm interested in seeing which disney movies are currently on streaming platforms, I want to examine the overlap between the two datasets:

```{r}
## Combining the Disney df and the df of movies on streaming platforms
disney.stream.now = inner_join(disney, stream.now, c('movie_title'='Title'))

## Making release_data a numerical variable
disney.stream.now$release_date = as.numeric(disney.stream.now$release_date)

## Getting rid of the rotton tomatoes column
disney.stream.now = disney.stream.now %>% select(-c('Rotten Tomatoes','Age'))

## To ensure that movies with same name also have same release date
disney.stream.now = disney.stream.now %>% filter(Year == release_date)

```


After this, I edited the dataset in excel. I added a column called:

'race': the race of the main characters that appear on the movie poster when googled - the race is separated by:
    white = characters' apparent races are white
    POC = characters appear to be people of color
    mixed = characters appear to be both white and POC

```{r}

## Adding race to the combined df (done in excel)
race.data = read_csv('New.data.add.csv')

## Only selecting columns with data
race.data = race.data %>% select(2:7) 

## Making race a factor variable
race.data$race = as.factor(race.data$race)

## Making sure to standardize the title column and to only have alphanumerics
race.data$movie_title = trimws(gsub("[^[:alnum:]]", " ", race.data$movie_title))

## Ommitting columns with NA
race.data = na.omit(race.data)

## Making a GGplot to explore relationships between variables 
ggpairs(aes(color = race), data = race.data, columns = 3:6, title = "Figure 1: Relationship between Disney Movies and Streaming Platform and Race Variables", legend = c(2,2)) 
```

Now, trying to see if find similar information in different datasets. Looking to see if similar data is found from grammy nominated songs and albums and popular music.

```{r}
## Downloading datasets
grammy.albums = read_csv('grammyAlbums_199-2019.csv')
grammy.songs = read_csv('grammySongs_1999-2019.csv')
top200 = read_csv('spotifyWeeklyTop200Streams.csv')
hot100 = read_csv('billboardHot100_1999-2019.csv')

## Tells how many times each artist was in the weekly top 200; groups by artist
top200_artist = top200_songs %>% group_by(Artist) %>% summarise(number_of_songs = n(), total_times_in_top200 = sum(times_in_top200), total_streams=sum(total_number_streams)) %>% ungroup()

## Tells how many times each song was in the weekly top 200 
top200_songs = top200 %>% select(everything()) %>% group_by(Name, Artist) %>% summarise(times_in_top200 = n(), total_number_streams = sum(Streams)) %>% ungroup()

```

A similar process as determining the race in the movies is performed here. The top200_artist df is extracted, and using excel, a race column is added. 

'race': the race of the singer/rapper/band members that appear on google images when googled - the race is separated by:
    white = artist/s apparent races is/are white
    POC = cartist/s apparent races is/are people of color
    mixed = artist/s apparent races is/are both white and POC


```{r}
## New df with race included
race.top200= read_csv('top200df.csv')

## Making sure to standardize Artist to only have alphanumerics
race.top200$Artist = trimws(gsub("[^[:alnum:]]", " ", race.top200$Artist))

## Making Artist a factor 
race.top200$Artist = as.factor(race.top200$Artist)

## Making race a factor and "mixed" into POC
race.top200$race = ifelse(race.top200$race == "mixed",'POC',race.top200$race)
race.top200$race = as.factor(race.top200$race)

## Plotting data to examine the density by race
ggplot(race.top200, aes(x = race, fill = 'hotpink')) + geom_bar() + ggtitle('Balance Between Races in Spotify Top 200 Dataset') + xlab('Race') + ylab('Count') 

```

The outcomes here show that the majority of singers are POC when including mixed people.These would be the successful singers as determined by repeats of their songs played.

We are now interested in seeing how an artist's instagram followers affects its classification. Therefore, we look at a new dataset. This new dataset has a list of artists, but also includes their gender and their number of followers at the time the data was recorded. 

```{r}
## Now we are intrigued at looking at followers too; Download this dataset
followers = read_csv('BillboardFromLast20/artistDf.csv')

## Deleting columns don't care about
followers = followers %>% select(c(2,3,7))

## Making sure to standardize to only have alphanumerics
followers$Artist = trimws(gsub("[^[:alnum:]]", " ", followers$Artist))

## Making artist a factor
followers$Artist = as.factor(followers$Artist)
```


Combining followers and gender information with the race dataset:

```{r}
## Combining followers and gender df with race data
followers.race = inner_join(race.top200, followers)

## Plotting data to examine the density by race
ggplot(followers.race, aes(x = race, fill = 'hotpink')) + geom_bar() + ggtitle('Balance Between Races in Spotify Top 200 Dataset Overlapped with Followers') + xlab('Race') + ylab('Count')
```

## Making a GGplot to explore relationships between variables 

Now I want to examine grammy song data, so going back to grammy song and album data. 

```{r}
## Only selecting columns interested in
grammy.songs = grammy.songs %>% select(-c(1,2))
grammy.albums = grammy.albums %>% select(-1)

## getting each artists # grammys nominated for songs and albumns
number.song.artist = grammy.songs %>% group_by(Artist) %>% summarise(Grammy.song.nom = n())
number.album.artist = grammy.albums %>% group_by(Artist) %>% summarise(Grammy.album.nom = n())

## Combining the overlap between the followers dataset and the number of songs each artist nominated for in Grammys

final1 = inner_join(number.song.artist, followers.race, c())
final1 = final1 %>% select(-c(number_of_songs,total_streams,total_times_in_top200,Gender))
final1 = final1[,c(1,2,4,3)]
final1$race = ifelse(final1$race =="white", 0, 1)

write_delim(final1, delim = ",", path = '/Users/maguina/Downloads/SML310/SML310-FinalProjectInfo/final1.csv') 

final2 = inner_join(followers.race,final1, c("Artist"))
final2 = final2 %>% select(-c(Grammy.song.nom,Gender))
final2 = final2 %>% select(-c(number_of_songs,total_times_in_top200,total_streams))
final2 = final2[,c(1,3,2)]
final2$race.x = ifelse(final2$race.x =="white", 0, 1)

write_delim(final2, delim = ",", path = '/Users/maguina/Downloads/SML310/SML310-FinalProjectInfo/final2.csv') 

## Making into df or excel
# write.xlsx(number.song.artist, file = '/Users/maguina/Downloads/SML310/FinalProject/number.song.artist.xlsx') 
# write_delim(number.album.artist, delim = ",", path = '/Users/maguina/Downloads/SML310/FinalProject/number.album.artist.csv') 
```




```{r}
## plots of race
    ggplot(race.top200, aes(x = race, y = total_times_in_top200, color = race)) + geom_boxplot()
    ggplot(race.top200, aes(x = race, y = number_of_songs, color = race)) + geom_boxplot()
    ggplot(race.top200, aes(x = race, y = total_streams, color = race)) + geom_boxplot()
    ggplot(race.top200, aes(x = number_of_songs, y = total_streams, group = race, color = race)) + geom_point() 

## plots of gender
ggplot(followers.race, aes(x = Gender, y = total_times_in_top200, color = Gender)) + geom_boxplot()
ggplot(followers.race, aes(x = Gender, y = number_of_songs, color = Gender)) + geom_boxplot()
ggplot(followers.race, aes(x = Gender, y = total_streams, color = Gender)) + geom_boxplot()
ggplot(followers.race, aes(x = number_of_songs, y = total_streams, group = Gender, color = Gender)) + geom_point()



```


---- redo this -- 

sum songs:
Women have a higher average of number of songs
Men have a higher maximum and more outliers

ignored mixed.. (add to data later)
- POC has higher average
- White has the maximum, but looks like POC has more higher values




total streams:
- women have a higher average of total streams
- men have more higher maximum streams than women

ignored mixed.. (add to data later)
- looks like about even
- White has the maximum
- POC have more higher valuyes it appears

---


Now want to examine gender and race
```{r}
data.soc = followers.race

data.soc$combo[(data.soc$Gender == 'F' & data.soc$race == 'POC')] = 'FPOC'
data.soc$combo[(data.soc$Gender == 'M' & data.soc$race == 'POC')] = 'MPOC'
data.soc$combo[(data.soc$Gender == 'F' & data.soc$race == 'white')] = 'Fwhite'
data.soc$combo[(data.soc$Gender == 'M' & data.soc$race == 'white')] = 'Mwhite'
data.soc$combo[(data.soc$Gender == 'F' & data.soc$race == 'mixed')] = 'Fmixed'
data.soc$combo[(data.soc$Gender == 'M' & data.soc$race == 'mixed')] = 'Mmixed'

data.soc$combo = as.factor(data.soc$combo)
data.soc$Gender = as.factor(data.soc$Gender)

## Cannot do ggpairs with data.soc because the categorical of mixed doesn't have enough observations

## Making new df for ggpairs
ok = data.soc %>% filter(combo != 'Mmixed', combo != 'Fmixed')
ggpairs(aes(color = combo), data = ok, columns = c(2,3,4,6,8))

ggpairs(aes(color = race), data = followers.race, columns = c(2,3,4,5,6,7), title = "Relationship between Spotify top 200 Artists, Followers, and Race Variables", legend = c(4,4))

```


```{r}
## Making df with rotten tomato
tomato = stream.now.orig %>% select(-c(X1, ID))
tomato = tomato %>% select(1:5)
tomato$Title = trimws(gsub("[^[:alnum:]]", " ", tomato$Title))
tomato.final = inner_join(disney, tomato, c('movie_title'='Title'))
tomato.final = tomato.final %>% filter(Year == release_date)
tomato.final$release_date = as.numeric(tomato.final$release_date)
tomato.final$movie_title = trimws(gsub("[^[:alnum:]]", " ", tomato.final$movie_title))
tomato.final = tomato.final %>% select(-c( release_date, Year, Age, inflation_adjusted_gross, IMDb))
tomato.final = full_join(race.data, tomato.final, c("movie_title"='movie_title'))

## rearranging the df so that race is last column
tomato.race = tomato.final[,c(1,2,3,4,5,7,6)]

## removing % from the columns
tomato.race$`Rotten Tomatoes` = trimws(gsub("[^[:alnum:]]", " ", tomato.race$`Rotten Tomatoes`))

## Renamming 'Rotten Tomatoes'
colnames(tomato.race)[6] = 'rotten'

## Saving to folder
write_delim(tomato.race, delim = ",", path = '/Users/maguina/Downloads/SML310/FinalProject/tomato.race.csv') 

```









